---
title: "Statistical Inference Course Project"
author: S Sagara
output:
  html_document: default
  pdf_document: default
---

This is 2 Basic inferential data analysis.

Load the ToothGrowth data
```{r}
library(datasets)
df <- ToothGrowth
#Summary statistics
summary(df)
#plot for len by supp in dose facets
#It appears that there is a positive correlation between len and dose.
library(ggplot2)
ggplot(df, aes(supp,len))+
        geom_boxplot(outlier.color = "red",fill="green") +
        facet_grid(.~dose)

#confidence intervals and/or hypothesis tests
df_oj <- df[df["supp"]=="OJ",]
df_oj_0.5 <- df_oj[df_oj["dose"]==0.5,]
df_oj_1.0 <- df_oj[df_oj["dose"]==1,]
df_oj_2.0 <- df_oj[df_oj["dose"]==2,]

df_vc <- df[df["supp"]=="VC",]
df_vc_0.5 <- df_vc[df_vc["dose"]==0.5,]
df_vc_1.0 <- df_vc[df_vc["dose"]==1,]
df_vc_2.0 <- df_vc[df_vc["dose"]==2,]
```
H0: There is no difference in len among doses.
Ha: There is difference in len among doses.
alpha = .05 in two sided test, thus .025 in one side
OJ

Supp OJ for dose between 0.5 and 1.0
H0 is rejected with p-value of 8.785e-05 and the test indicates there is difference.
95% Confidence interval is (-13.415634  -5.524366).
```{r echo=F}
t.test(df_oj_0.5$len, df_oj_1.0$len,var.equal = F)
```
Supp OJ for dose between 0.5 and 2.0
H0 is rejected with p-value of 1.324e-06 and the test indicates there is difference.
95% Confidence interval is (-16.335241  -9.324759)
```{r echo=F}
t.test(df_oj_0.5$len, df_oj_2.0$len,var.equal = F)
```
Supp OJ for dose between 1.0 and 2.0
H0 cannot be rejected with p-value of 0.0392, which is higher than .025.
95% Confidence interval is (-6.5314425 -0.1885575).
```{r echo=F}
t.test(df_oj_1.0$len, df_oj_2.0$len,var.equal = F)
```
VC
Supp VC for dose between 0.5 and 1.0
H0 is rejected with p-value of 6.811e-07 and the test indicates there is difference.
95% Confidence interval is (-11.265712  -6.314288).
```{r echo=F}
t.test(df_vc_0.5$len, df_vc_1.0$len,var.equal = F)
```
Supp VC for dose between 0.5 and 2.0
H0 is rejected with p-value of 4.682e-08 and the test indicates there is difference.
95% Confidence interval is (-21.90151 -14.41849).
```{r echo=F}
t.test(df_vc_0.5$len, df_vc_2.0$len,var.equal = F)
```
Supp VC for dose between 1.0 and 2.0
H0 is rejected with p-value of 9.156e-05 and the test indicates there is difference.
95% Confidence interval is (-13.054267  -5.685733).
```{r echo=F}
t.test(df_vc_1.0$len, df_vc_2.0$len,var.equal = F)
```
In conclusion, the null hypothesis of no difference in len by supp among doses is rejected, 
except OJ len between dose 1 and 2, and as a result, it would be reasonable to assume there is indeed
difference in len among doses statistically.
