---
title: "Statistical Inference Course Project"
author: S Sagara
output:
  html_document: default
  pdf_document: default
---
This is 1 A simulation exercise.

```{r}
#The 1000 exponential simulations are run 40 times and the average of the simulatons is calculated.
mns = NULL
for (i in 1 : 40) mns = c(mns, mean(rexp(1000,0.2)))
```
```{r}
simulation.mean <- mean(mns)
theoretical.mean <- 1/0.2
```
Difference between simulation mean and theoretical mean
The calculation shows that the simulation mean is very close to the theoretical mean.
```{r}
simulation.mean - theoretical.mean
```
Variance of simulation
The 1000 exponential simulations are run 40 times and the variance of the simulatons is calculated.
```{r}
vns = NULL
for (i in 1 : 40) vns = c(vns, var(rexp(1000,0.2)))
simulation.var <- mean(vns)
```
Variance of theoretical distribution
```{r}
theoretical.std <- 1/0.2
theoretical.var <- theoretical.std^2
```
Difference between simulation variance and theoretical variance
The calculations shows that the simulation variance is very close to the theoretical variance.
```{r}
simulation.var - theoretical.var
```
Distribution of sample mean is approximately normal as the peak of the histogram is aroung the mean and the shape of the graph is bell-shape.
```{r}
hist(mns,xlab = "Exponential Mean")
```